On Secure Delegation of SampBQP with a Classical Client

### 2020-04-07 qpip.tex
Add clarification
Add details for SampBQP soundness proof

Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
It is simple to check that $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
We now show its completeness and soundness.

@@

	Now we show soundness.
	Suppose $\PSampstar$ is a cheating prover that sends some $\sigma$ to the verifier.

@@

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate $\sigma'$ with a classical mix over tensors of independent states.
	That is, there exists some $\rho=\sum_j w_j\rho_j^{\otimes m+1}$
	\Ethan{multiple copies to one copy? Say in words that rho j is one component of iids}
	such that for all quantum-classical channels $\Lambda_i$ on $n+T+\frac{T}{\varepsilon}$ qubits:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
	\leq\sqrt{\frac{2m^2\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
	=O(\varepsilon).$$

	\Ethan{In our context, lambda i is ground state check... etc. and rho 1 rho 2 are...}

	Let $p_j$ be the probability that $\cVGS(\rho_j)=acc$. Now we seperate the $\rho_j$ terms into two categories based on $p_j$.

	First suppose $p_j<\frac{1}{2}-2\kappa$,
	then a standard Chernoff bound argument can be applied show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.

    \Ethan{TODO Fix the kets}

	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\rho_j$ and $\psi_{C'(x)}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\rho_j, \psi_{C'(x)})\geq1-\varepsilon^2.$$
	which in turn implies a lower bound on the respective trace distance:
	$$\frac{1}{2}\norm{\rho_j - \ket{\psi_{C'(x)}}}_1<\varepsilon.$$

	The probability of measuring $t<T$ on the clock register of $\ket{\phi_{C'(x)}}$ is $O(\varepsilon)$ due to the padding,
	so the data register has $1-O(\varepsilon)$ probability to be $C(x)$ at this point.

	The soundness errors at each step is $O(\varepsilon)$, so the conclusion follows.
	\Ethan{Be more careful here. Actually sum up errors.}
\end{prf}

>>>>

Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
It is simple to check that $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
We now show its completeness and soundness.
Particularly, we prove that it has $O(\varepsilon)$ soundness errors
with the understanding that by relabelling $\varepsilon'=O(\varepsilon)$ and modifying $\PiSamp$ accordingly,
one can achieve $\varepsilon'$ soundness errors while maintaining completeness and running time properties.

@@

	Now we show soundness.

	Suppose $\PSampstar$ is a cheating prover that sends some $\sigma$ to the verifier.

@@

	\Ethan{Trace out discarded copy on $\sigma'$? Or add copies on $\tau$?}

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $M$-fold tensor products of identical copies of some states $\tau_j$.
	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes M}$
	such that for all quantum-classical channels $\Lambda_i$ acting on registers with size of $\ket{\psi_{C'(x)}}$:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
	\leq\sqrt{\frac{2m^2\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
	=O(\varepsilon).$$
	In our context, for $1\leq i\leq m$, $\Lambda_i$ corresponds to measurements chosen by $\cVGS$.
	$\Lambda_{m+1}$ is measurement on the data register of $\rho_k$.

	Now we claim that for each component $\tau_j$,
	if $\PSampstar$ had sent $\tau_j^{\otimes M}$ instead then the soundness error is $O(\varepsilon)$.
	Let $p_j$ be the probability that $\cVGS(\tau_j)=acc$, we seperate $\tau_j$ terms into two cases.

	First suppose $p_j<\frac{1}{2}-2\kappa$,
	then a standard Chernoff bound argument can be applied show that this case has negligible acceptance probabilities.
	That is, it outputs $(rej, \bot)$ with overwhelming probability, hence has negligible soundness errors.

	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\tau_j$ and $\ket{\psi_{C'(x)}}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\tau_j, \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}})\geq1-\varepsilon^2.$$
	which in turn implies a lower bound on the respective trace distance:
	$$\frac{1}{2}\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_1<\varepsilon.$$
	Let $(d, y)$ be $\VSamp$'s output. Suppose $d=acc$, then $y$ would be the measurement on $\tau_j$'s data register,
	which is $\varepsilon$-close to that on $\ket{\psi_{C'(x)}}$.
	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has $1-\varepsilon$ probability to contain $C(x)$ due to the padding.
	So $y$ is $O(\varepsilon)$-close to $y_{ideal}$ when $d=acc$.
	Which implies that $(d, y)$ is $O(\varepsilon)$-close to $(d, y_{ideal})$.

	The cheating prover's strategies corresponding to $\tau_j$ all have $O(\varepsilon)$ soundness errors.
	As $\rho$ is a convex combination of these strategies, we conclude the same about it.
	Finally, as the outputs corresponding to $\sigma$ is $\varepsilon$-close to that of some $\rho$,
	by data processing inequality we conclude that $\PiSamp$ has $O(\varepsilon)$ soundness errors.
\end{prf}
